Text embedding models yield high resolution insights into conceptual knowledge from short multiple choice quizzes

### 2023-02-01 paper/main.tex

We fetched these automated transcripts using the \texttt{youtube-transcript-api} 
Python package (\textcolor{red}{\textbf{Jeremy can you add a citation for this?} 
https://github.com/jdepoix/youtube-transcript-api}). The transcripts consisted of 
one timestamped line of text for every few seconds (mean: 2.34s; standard 
deviation: 0.83s) of spoken content in the video (i.e., corresponding to each 
individual caption that would appear on-screen if viewing the lecture via YouTube, 
and when those lines would appear). We
defined a sliding window length of (up to) $w = 30$ transcript lines, and
assigned each window a timestamp corresponding to the midpoint between its first
and last lines' timestamps. These sliding windows ramped up and down in length
at the very beginning and end of the transcript, respectively. In other words,
the first sliding window covered only the first line from the transcript; the
second sliding window covered the first two lines; and so on. This insured that
each line of the transcript appeared in the same number ($w$) of sliding
windows. After performing various standard text preprocessing (e.g., normalizing case, 
lemmatizing, removing punctuation and stop-words), we treated the text from each 
sliding window as a single ``document,''
and we combined these documents across the two videos' windows to create a single
training corpus for the topic model.  The top words from each of the 15 discovered
topics may be found in Table~\topics.

@@

\begin{equation}
    \mathrm{ncorr}(x, y) = \frac{\mathrm{corr}(x, y) - \mathrm{mincorr}}{\mathrm{maxcorr} - \mathrm{mincorr}},
\end{equation}

and where $\mathrm{mincorr}$ and $\mathrm{maxcorr}$ are the minimum and maximum
correlations between any lecture timepoint and question, taken over all
timepoints and questions across both lectures and all five question used to
estimate the knowledge trace \textcolor{red}{\textbf{Note: make sure this is
correct in results section; not sure i caught all instances}}. We also define
$f(s, \Omega)$ as the $s$\textsuperscript{th} topic vector from the set of
topic vectors $\Omega$. Here $t$ indexes the set of lecture topic vectors, $L$,
and $i$ and $j$ index the topic vectors of questions used to estimate the
knowledge trace, $Q$. Note that ``correct'' denotes the set of indices of the
questions the participant answered correctly on the given quiz.

>>>>

We fetched these automated transcripts using the
\texttt{youtube-transcript-api} Python package~\citep{Depo19}. The transcripts
consisted of one timestamped line of text for every few seconds (mean: 2.34~s;
standard deviation: 0.83~s) of spoken content in the video (i.e., corresponding
to each individual caption that would appear on-screen if viewing the lecture
via YouTube, and when those lines would appear). We defined a sliding window
length of (up to) $w = 30$ transcript lines, and assigned each window a
timestamp corresponding to the midpoint between its first and last lines'
timestamps. These sliding windows ramped up and down in length at the very
beginning and end of the transcript, respectively. In other words, the first
sliding window covered only the first line from the transcript; the second
sliding window covered the first two lines; and so on. This insured that each
line of the transcript appeared in the same number ($w$) of sliding windows.
After performing various standard text preprocessing (e.g., normalizing case,
lemmatizing, removing punctuation and stop-words), we treated the text from
each sliding window as a single ``document,'' and we combined these documents
across the two videos' windows to create a single training corpus for the topic
model. The top words from each of the 15 discovered topics may be found in
Table~\topics.

@@

\begin{equation}
    \mathrm{ncorr}(x, y) = \frac{\mathrm{corr}(x, y) - \mathrm{mincorr}}{\mathrm{maxcorr} - \mathrm{mincorr}},
\end{equation}
and where $\mathrm{mincorr}$ and $\mathrm{maxcorr}$ are the minimum and maximum
correlations between any lecture timepoint and question, taken over all
timepoints and questions across both lectures and all five question used to
estimate the knowledge trace. We also define $f(s, \Omega)$ as the
$s$\textsuperscript{th} topic vector from the set of topic vectors $\Omega$.
Here $t$ indexes the set of lecture topic vectors, $L$, and $i$ and $j$ index
the topic vectors of questions used to estimate the knowledge trace, $Q$. Note
that ``correct'' denotes the set of indices of the questions the participant
answered correctly on the given quiz.
